Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/example.tex
remove finished todos

\subsection{An Example from the Scala Collections Library}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMinted{java}{collectionsExample.java}
\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} is an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them. At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
One could design an IFDS analysis to detect this kind of bug.

>>>>

\subsection{An Example from the Scala Collections Library}
The Scala collections library contains the trait \code{TraversableOnce} that is
shared by both collections and iterators over them. The \code{toArray} method of this trait
creates an array and copies the contents of the collection or iterator into it:
\inputMinted{java}{collectionsExample.java}
%\otodo{Marianna, can you figure out how to get LaTeX to syntax-highlight this?} 
When \code{this} is an iterator rather than a collection, the call to \code{this.size}
extracts all elements of the iterator to count them. At the call to \code{copyToArray},
the iterator is already empty, so nothing is copied to the newly created array.
One could design an IFDS analysis to detect this kind of bug.
